Large squeezing in Bose-Einstein condensates with large numbers of atoms

### 2013-07-18 large_number_squeezing_with_atoms.tex
Simplifying language and converting some US-isms to Australian English for consistency.

The system is prepared with all the population initially in $|a\rangle$, and vacuum in $|b\rangle$. We choose the initial state $|a\rangle$ to be a coherent state with average number $\langle \hat{a}^{\dagger} \hat{a} \rangle = N$, where $N$ is the total particle number.  As the system is insensitive to the initial phase of the coherent state, this is equivalent to a mixture of coherent states of uncertain phase, or a mixture of Poissonian-distributed number states. Such a state is consistent with BEC coherence experiments \cite{Hadzibabic2004}.

@@

In Figure \ref{figTwoModeAnalyticExamples} we plot a solution for the normalized number variance in mode $|a\rangle$ as a function of $\phi$, choosing a typical set of nonlinearities. This example illustrates the basic features of the system: during the final coupling period, the normalised number variance undergoes cyclic variation with a period $\tau=\pi / \Omega$, and has a series of minima. It is necessary to choose both the correct phase $\phi$ as well as the correct length of time for the coupling to be applied in order to obtain optimum squeezing.

@@

\begin{figure}
    \centering
    \includegraphics[width=8cm]{figures/modal_squeezing_effects_1D.eps}
    \caption{Effects of mode shape on squeezing. The plot shows the normalized number variance in mode $|a \rangle$ as a function of the time the final coupling pulse is applied. We compare the analytic two-mode solution (thick red), the constant density mode (solid blue), the Thomas-Fermi mode (dashed) and the Gaussian mode (dash-dotted). The nonlinearities of the various 1D simulations have been adjusted for their mode shape so that they are equivalent to that of the 0D, two-mode mode nonlinearity. Parameters used were $n_a = n_b =1 \times 10^5$, $\chi_{aa}=0.03 \text{s}^{-1}, \chi_{ab}=\chi_{bb}=0, \tau_{\mathrm{hold}}=3\times 10^{-4}$s, $\phi=4.0$. Maximum squeezing is achieved when the atomic density profile is the most uniform.}
    \label{figModalSqueezingEffects1D}
\end{figure}

@@

where we have defined $\lambda_{ij} = \chi_{ij} (t_2-t_1)$. Utilizing (\ref{eqHadamard}) to move $\hat{a}_1$ through the exponential, with some algebra one can show that

@@

Finally, to obtain $\hat{a}_3$ and $\hat{b}_3$ we utilize (\ref{eqa1}) and (\ref{eqb1}) with the phase factor attached to the $\hat{b}$ operator to obtain

>>>>

The system is prepared with all the population initially in $|a\rangle$, and vacuum in $|b\rangle$. We choose the initial state $|a\rangle$ to be a coherent state with average number $\langle \hat{a}^{\dagger} \hat{a} \rangle = N$.  As the system is insensitive to the initial phase of the coherent state, this is equivalent to a mixture of coherent states of uncertain phase, or a mixture of Poisson-distributed number states. Such a state is consistent with BEC coherence experiments \cite{Hadzibabic2004}.

@@

In Figure \ref{figTwoModeAnalyticExamples} we plot a solution for the normalised number variance in mode $|a\rangle$ as a function of $\phi$, choosing a typical set of nonlinearities. This example illustrates the basic features of the system: during the final coupling period, the normalised number variance undergoes cyclic variation with a period $\tau=\pi / \Omega$, and has a series of minima. It is necessary to choose both the correct phase $\phi$ as well as the correct length of time for the coupling to be applied in order to obtain optimum squeezing.

@@

\begin{figure}
    \centering
    \includegraphics[width=8cm]{figures/modal_squeezing_effects_1D.eps}
    \caption{Effects of mode shape on squeezing. The plot shows the normalised number variance in mode $|a \rangle$ as a function of the time the final coupling pulse is applied. We compare the analytic two-mode solution (thick red), the constant density mode (solid blue), the Thomas-Fermi mode (dashed) and the Gaussian mode (dash-dotted). The nonlinearities of the various 1D simulations have been adjusted for their mode shape so that they are equivalent to that of the 0D, two-mode mode nonlinearity. Parameters used were $n_a = n_b =1 \times 10^5$, $\chi_{aa}=0.03 \text{s}^{-1}, \chi_{ab}=\chi_{bb}=0, \tau_{\mathrm{hold}}=3\times 10^{-4}$s, $\phi=4.0$. Maximum squeezing is achieved when the atomic density profile is the most uniform.}
    \label{figModalSqueezingEffects1D}
\end{figure}

@@

where we have defined $\lambda_{ij} = \chi_{ij} (t_2-t_1)$. Using (\ref{eqHadamard}) to move $\hat{a}_1$ through the exponential, with some algebra one can show that

@@

Finally, to obtain $\hat{a}_3$ and $\hat{b}_3$ we use (\ref{eqa1}) and (\ref{eqb1}) with the phase factor attached to the $\hat{b}$ operator to obtain
